The SMT Competition 2015--2018

### 2019-08-30 2018/report/table-winners-main.tex
Division without solvers was non-competitive

\begin{table}
\caption{Best \maintrack solvers (by division).}
\label{tab:winners-main}
\centering
\scalebox{.755}{%
\renewcommand{\arraystretch}{1.01}%

@@

QF\_ABVFP   &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{---} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\

>>>>

\begin{table}
\caption{Best \maintrack solvers (by division)}
\label{tab:winners-main}
\centering
\scalebox{.755}{%
\renewcommand{\arraystretch}{1.01}%

@@

QF\_ABVFP   &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc ---} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} \\
